---
title: "Health-Related Social Influence Strategies in Overweight Romantic Couples: Daily Associations with Physical Activity and Affect for Targets and Actors "
author: "Pascal Küng, MSc (ORCID: 0000-0001-7346-9414), Corina Berli, PhD (ORCID: 0000-0002-5078-3539), Patrick S. Höhener, MSc (ORCID: 0000-0003-3635-2799), Robert Tobias, PhD (ORCID: 0000-0001-7972-122X), Urte Scholz, PhD (ORCID: 0000-0003-0184-5921)"
date: "`r Sys.Date()`"
output: 
  html_document: 
    df_print: kable
    toc: yes
    toc_float: yes
    code_folding: show
    toc_depth: 5
---



# Setup and loading

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
options(dplyr.print_max = 100)

library('ggplot2')
library('nlme')
library('MASS')
library('haven')
library('scales')
library('cowplot')
library('devtools')
library('ggResidpanel')
library('lme4')
library('glmmTMB')
library('DHARMa')
library('ggeffects')
library('broom.mixed')
library('easystats')
library('Hmisc')
library('bmlm')
library('tidyverse')
library('wbCorr')
library('psych')
library('report')
library('lavaan')
library('basicPlotteR')
library('misty')
library('dplyr')

# importing data
DF <- haven::read_sav("C:/Users/kueng/OneDrive - Universität Zürich UZH/04 Papers/01 Dyactic Paper/Datensätze/DyadicDiaryT3T0+Acc_4Feld_200527.sav")
df_baseline_target <- haven::read_sav("C:/Users/kueng/OneDrive - Universität Zürich UZH/04 Papers/01 Dyactic Paper/Datensätze/DYACTIC_T0Zielperson_A_141118.sav")
df_baseline_agent <- haven::read_sav("C:/Users/kueng/OneDrive - Universität Zürich UZH/04 Papers/01 Dyactic Paper/Datensätze/DYACTIC_T0PartnerIn_B_141118.sav")

# Keep only the 99 individuals that provided follow-up data
df_baseline_target <- df_baseline_target[df_baseline_target$ID %in% unique(DF$ID), ]
df_baseline_agent <- df_baseline_agent[df_baseline_agent$ID %in% unique(DF$ID), ]

df <- DF %>% 
  mutate(
    intention_agent_lagged = as.numeric(Lag(pbyint99)), 
    self_efficacy_agent_lagged = as.numeric(Lag(pbyswe99)),
    plan_agent_lagged = as.numeric(Lag(pbypla99)), 
    risk_perception_agent = as.numeric(pbyris99), 
    perceived_benfeits_agent = as.numeric(pbyout99), 
    
    intention_target_lagged = as.numeric(Lag(sbyint99)), 
    self_efficacy_target_lagged = as.numeric(Lag(sbyswe99)),
    plan_target_lagged = as.numeric(Lag(sbypla99)), 
    risk_perception_target = as.numeric(sbyris99), 
    perceived_benfeits_target = as.numeric(sbyout99)
  ) 


```

```{r loading_datasets, results='hide'}

df$CoupleID <- as.factor(df$CoupleID)

# Subsetting only the target person. 
df <- df[(df["sbyz_p"] == 1), ]

  
```

# Describe sample

## Target's health
```{r target_health}
# Add PA risk assessment to df

df_baseline_target <- df_baseline_target %>% 
  mutate(
    parq_score = rowMeans(across(c(sb0prq01, sb0prq02, sb0prq03, sb0prq04, sb0prq05, sb0prq06, sb0prq08)), na.rm = TRUE),
    n_health_issues = rowSums(across(c(sb0prq01, sb0prq02, sb0prq03, sb0prq04, sb0prq05, sb0prq06, sb0prq08)), na.rm = TRUE),
    has_zero_issues = as.factor(ifelse(n_health_issues == 0, 1, 0)),
    has_heart_condition = as.factor(sb0prq01), 
    has_chest_pain = as.factor(sb0prq02),
    has_breathing_issues = as.factor(sb0prq03), 
    has_dizziness_or_fainting = as.factor(sb0prq04), 
    has_joint_or_bone_problems = as.factor(sb0prq05), 
    takes_heart_medications = as.factor(sb0prq06), 
    has_other_health_issues = as.factor(sb0prq08), 
    other_health_issue = as.character(sb0prq07),
    other_health_issue = as.factor(ifelse(
      other_health_issue %in% c('faulheit', 'Keine Motivation (Faulheit)', 'Zeitmangel', 'Übergewicht', 'übergewicht'),
      NA, other_health_issue)),
    has_diabetes = as.factor(sb0prq09)
  ) %>% 
  dplyr::select(parq_score, n_health_issues, has_zero_issues, has_heart_condition, has_chest_pain, 
         has_breathing_issues, has_dizziness_or_fainting, has_joint_or_bone_problems, 
         takes_heart_medications, has_diabetes, has_other_health_issues, other_health_issue)


a <- as.data.frame(report::report_table(df_baseline_target)[, c('Variable', 'Level', 'n_Obs', 'percentage_Obs', 'Mean', 'SD', 'Min', 'Max')])

a[a$Level != 0,]

hist(df_baseline_target$n_health_issues)


```


## Agent's health
```{r agent_health}
# Add PA risk assessment to df

df_baseline_agent <- df_baseline_agent %>% 
  mutate(
    parq_score = rowMeans(across(c(pb0prq01, pb0prq02, pb0prq03, pb0prq04, pb0prq05, pb0prq06, pb0prq08)), na.rm = TRUE),
    n_health_issues = rowSums(across(c(pb0prq01, pb0prq02, pb0prq03, pb0prq04, pb0prq05, pb0prq06, pb0prq08)), na.rm = TRUE),
    has_zero_issues = as.factor(ifelse(n_health_issues == 0, 1, 0)), 
    has_heart_condition = as.factor(pb0prq01), 
    has_chest_pain = as.factor(pb0prq02), 
    has_breathing_issues = as.factor(pb0prq03), 
    has_dizziness_or_fainting = as.factor(pb0prq04), 
    has_joint_or_bone_problems = as.factor(pb0prq05), 
    takes_heart_medications = as.factor(pb0prq06), 
    has_other_health_issues = as.factor(pb0prq08), 
    other_health_issue = as.character(pb0prq07),
    other_health_issue = as.factor(ifelse(
      other_health_issue %in% c('faulheit', 'Keine Motivation (Faulheit)', 'Zeitmangel', 'Übergewicht', 'übergewicht'),
      NA, other_health_issue)),
    has_diabetes = as.factor(pb0prq09))  %>% 
  dplyr::select(parq_score, n_health_issues, has_zero_issues, has_heart_condition, has_chest_pain, 
       has_breathing_issues, has_dizziness_or_fainting, has_joint_or_bone_problems, 
       takes_heart_medications, has_diabetes, has_other_health_issues, other_health_issue)


b <- as.data.frame(report::report_table(df_baseline_agent)[, c('Variable', 'Level', 'n_Obs', 'percentage_Obs', 'Mean', 'SD', 'Min', 'Max')])


b[b$Level != 0,]


hist(df_baseline_agent$n_health_issues)


```


## Joint health
```{r jointhealth}
# Add PA risk assessment to df

df_baseline_joint <- rbind(df_baseline_target, df_baseline_agent)


c <- as.data.frame(report::report_table(df_baseline_joint)[, c('Variable', 'Level', 'n_Obs', 'percentage_Obs', 'Mean', 'SD', 'Min', 'Max')])

c[c$Level != 0,]


hist(df_baseline_joint$n_health_issues)


```



## Other sample Statistics

```{r samplestats}

infodf <- df[,c('sb0sex01', 'pb0sex01', 
      'group', #group 1 + 2 = EG, 3 + 4 = KG
      'sb0age01', 'pb0age01', 
      'sb0edu01', 'pb0edu01', # welchen höchsten Bildungsabschluss haben Sie?
      'sb0aus01', 'pb0aus01', # Was ist ihre Berufsausbildung?
      'sb0occ01', 'pb0occ01', # Sie sind zur Zeit? (occupation)
      'sb0bez_r', # Dauer Beziehung in Jahren
      'sb0woh_r', # Dauer zusammen wohnen in Monaten
      'sb0ziv01', #verheiratet?
      'sb0kid01', # Kinder mit derzeitigem Parnter?
      'sb0kiz01', # wie viele Kinder?
      'sb0kih01', # Lebt min. 1 Kind in Haushalt?
      'sb0net01', # Monatliches Netto Einkommen des Haushalts
      'sb0bmi', # bmi target
      'pb0bmi', # bmi agent
      'sb0matur', # matura target
      'pb0matur' # matura agent
      )]

infodf$sb0woh_r <- infodf$sb0woh_r / 12

infodfunlabelled <- infodf %>%
  mutate(across(where(is.labelled), as_factor)) %>%
  as.data.frame(report_ta)
  
sample_df <- as.data.frame(report_table(infodfunlabelled))

# export to excel

writexl::write_xlsx(sample_df, "sample description.xlsx")

```

```{r rangediary}
# Date of diary days
range(df$sbwdat01, na.rm = T)

```

# Data wrangling

## Calculating Scores
First, we compute the reliability of our scales
### Reliability within and between person for persuasion

```{r omega1, warning=FALSE}

# Function to compute within- and between- omega
omega_multilevel <- function(data, variables, cluster_var = "CoupleID", fiml = TRUE, ci = 0.95) {
  #' This function computes omega reliability coefficients for multilevel data.
  #' It fits a two-level CFA model using lavaan and calculates omega coefficients for both within-cluster and between-cluster levels.
  #' 
  #' Inputs:
  #' - data: A data frame containing the variables for analysis.
  #' - variables: A character vector of variable names to include in the model.
  #' - cluster_var: Name of the clustering variable (default: "CoupleID").
  #' - fiml: If TRUE, uses Full Information Maximum Likelihood for missing data (default: TRUE).
  #' - ci: Confidence level for intervals (default: 0.95).
  #' 
  #' Returns a list containing:
  #' - omegas: Data frame with omega estimates, standard errors, and confidence intervals.
  #' - fit_indices: Model fit indices (chi-square, df, p-value, CFI, TLI, RMSEA, SRMR).
  #' - model: The lavaan model specification.
  #' - full_summary: Full summary output from the lavaan model.
  #' 
  #' The function uses robust maximum likelihood estimation (MLR) and computes confidence intervals using the delta method.
  #' At least two variables are required for the model.  
  # Error checking
  if(length(variables) < 2) {
    stop("At least two variables are required for the model.")
  }
  
  # Create the model string
  model_parts <- lapply(seq_along(variables), function(i) {
    var <- variables[i]
    c(
      sprintf("f_within =~ wl%d*%s", i, var),
      sprintf("%s ~~ wr%d*%s", var, i, var),
      sprintf("f_between =~ bl%d*%s", i, var),
      sprintf("%s ~ 1", var),
      sprintf("%s ~~ br%d*%s", var, i, var),
      sprintf("wr%d > 0", i),
      sprintf("br%d > 0", i)
    )
  })
  
  model <- c(
    "# Within level",
    "level: 1",
    unlist(lapply(model_parts, `[`, 1:2)),
    "",
    "# Between level",
    "level: 2",
    unlist(lapply(model_parts, `[`, 3:5)),
    "",
    "# Defined parameters for omega calculation",
    sprintf("num_within := (%s)^2", paste0("wl", seq_along(variables), collapse = " + ")),
    sprintf("denom_within := (%s)^2 + (%s)", 
            paste0("wl", seq_along(variables), collapse = " + "),
            paste0("wr", seq_along(variables), collapse = " + ")),
    "omega_within := num_within / denom_within",
    "",
    sprintf("num_between := (%s)^2", paste0("bl", seq_along(variables), collapse = " + ")),
    sprintf("denom_between := (%s)^2 + (%s)", 
            paste0("bl", seq_along(variables), collapse = " + "),
            paste0("br", seq_along(variables), collapse = " + ")),
    "omega_between := num_between / denom_between",
    "",
    "# Constraints",
    unlist(lapply(model_parts, `[`, 6:7))
  )
  
  model <- paste(model, collapse = "\n")
  
  # Fit the model
  fit <- tryCatch({
    lavaan::sem(
      model, 
      data = data, 
      cluster = cluster_var, 
      estimator = "MLR", 
      missing = if(fiml) "fiml" else "listwise", 
      std.lv = TRUE, 
      auto.fix.first = FALSE, 
      auto.var = FALSE,
      se = "robust"
    )
  }, error = function(e) {
    stop("Error in fitting the model: ", e$message)
  })
  
  # Extract results
  summary_fit <- summary(fit)
  omegas <- summary_fit$pe[summary_fit$pe$label %in% c('omega_within', 'omega_between'), ]
  
  # Calculate confidence intervals
  z_score <- qnorm((1 + ci) / 2)
  omegas$ci.lower <- omegas$est - z_score * omegas$se
  omegas$ci.upper <- omegas$est + z_score * omegas$se
  
  # Select relevant columns
  omegas <- omegas[, c('label', 'est', 'se', 'ci.lower', 'ci.upper')]
  rownames(omegas) <- omegas$label
  omegas$label <- NULL
  
  # Ensure CI bounds are within [0, 1]
  omegas$ci.lower <- pmax(0, pmin(1, omegas$ci.lower))
  omegas$ci.upper <- pmax(0, pmin(1, omegas$ci.upper))
  
  fit_indices <- fitMeasures(fit, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "srmr"))
  
  # Return results
  list(
    omegas = omegas,
    fit_indices = fit_indices,
    model = model,
    full_summary = summary_fit
  )
}


```



Calculating Scores by taking the mean of the applicable items. "target"
is the person that receives control. - "agent" is the person that uses
control (but also support)

```{r scores}

# Predictors
df$PSC_agent <- (df$ppysko06 + df$ppysko09 + df$ppysko21 + df$ppysko25) / 4
df$NSC_agent <- (df$ppysko03 + df$ppysko11 + df$ppysko26 + df$ppysko29) / 4

# Outcomes
df$Paff_agent <- (df$pbypan03 + df$pbypan14 + df$pbypan09 + df$pbypan12 + df$pbypan16) / 5
df$Naff_agent <- (df$pbypan02 + df$pbypan04 + df$pbypan07 + df$pbypan15 + df$pbypan19) / 5

df$Paff_target <- (df$sbypan03 + df$sbypan14 + df$sbypan09 + df$sbypan12 + df$sbypan16) / 5
df$Naff_target <- (df$sbypan02 + df$sbypan04 + df$sbypan07 + df$sbypan15 + df$sbypan19) / 5

# Covariates
## Social Support
df$Sup_target <- (df$sbysug99 + df$sbysug98) / 2
df$Sup_agent <- (df$pbysug99 + df$pbysug98) / 2


# preparing covariates for sensitivity Analysis
# mean for time spent together from each partners report. 
df$time_spent <- df$sbytim99 + df$pbytim99 / 2
# renaming variables that have to be centered
df <- transform(df, 
                reldur = sb0bez_r, 
                sage = sb0age01, 
                page = pb0age01, 
                sbmi = sb0bmi, 
                pbmi = pb0bmi
                )


# Filtering out days with low wear compliance
df <- df %>% 
  mutate(sbwmvpa01 = ifelse(sbwwear > 10, sbwmvpa01, NA),
         pbwmvpa01 = ifelse(pbwwear > 10, pbwmvpa01, NA)
         )

head(df)


```

```{r omega2, warning = FALSE}
# Define the variable sets for each construct

persuasion_vars <- c('ppysko06', 'ppysko09', 'ppysko21', 'ppysko25') #25, 21, (6)
pressure_vars <- c('ppysko03', 'ppysko11', 'ppysko26', 'ppysko29') # 03, 26
paff_agent_vars <- c("pbypan03", "pbypan14", "pbypan09", "pbypan12", "pbypan16")
naff_agent_vars <- c("pbypan02", "pbypan04", "pbypan07", "pbypan15", "pbypan19")
paff_target_vars <- c("sbypan03", "sbypan14", "sbypan09", "sbypan12", "sbypan16")
naff_target_vars <- c("sbypan02", "sbypan04", "sbypan07", "sbypan15", "sbypan19")

naff_both_vars <- c(naff_agent_vars, naff_target_vars)
paff_both_vars <- c(paff_agent_vars, paff_target_vars)


sup_target_vars <- c("sbysug99", "sbysug98")
sup_agent_vars <- c("pbysug99", "pbysug98")

# Fit models for each construct
# Persuasion
fit <- omega_multilevel(data = df, variables = persuasion_vars)
print(round(fit$omegas, 2))
# Pressure
fit <- omega_multilevel(data = df, variables = pressure_vars)
print(round(fit$omegas, 2))

# Positive Affect both
fit <- omega_multilevel(data = df, variables = paff_both_vars)
print(round(fit$omegas, 2))
# Negative Affect both
fit <- omega_multilevel(data = df, variables = paff_both_vars)
print(round(fit$omegas, 2))

# Positive Affect Agent
#fit <- omega_multilevel(data = df, variables = paff_agent_vars)
#print(round(fit$omegas, 2))
# Negative Affect Agent
#fit <- omega_multilevel(data = df, variables = naff_agent_vars)
#print(round(fit$omegas, 2))
# Positive Affect Target
#fit <- omega_multilevel(data = df, variables = paff_target_vars)
#print(round(fit$omegas, 2))
# Negative Affect Target
#fit <- omega_multilevel(data = df, variables = naff_target_vars)
#print(round(fit$omegas, 2))


fit <- multilevelTools::omegaSEM(
  sup_target_vars,
  'CoupleID',
  data = df
)

fit

```



Checking reliability with different combinations of items. 

```{r}

best_reliability <- function(vars) {
  # Placeholder for results
  results <- list()

  # Loop through combinations of 2 or more constructs
  for (n in 2:length(vars)) {
    combinations <- combn(vars, n, simplify = FALSE)
    
    for (combo in combinations) {
      # Run omegaSEM on the current combination
      fit <- try(multilevelTools::omegaSEM(
        combo,
        'CoupleID',
        data = df
      ), silent = TRUE)
      
      # Store results
      if (!inherits(fit, "try-error")) {
        results[[paste(combo, collapse = "_")]] <- fit
      } else {
        cat("Error in combination:", paste(combo, collapse = "_"), "\n")
      }
    }
  }
  
  # Print results
  results
}


best_reliability(persuasion_vars)
best_reliability(pressure_vars)

```



The original study assigned couples to interventions vs. control groups.
In this followup study, we would like to still have more or less equal
group sizes.

```{r chekgroups}

# Combine control groups (3 and 4) and set them to 0.
df$group[df$group %in% c(3, 4)] <- 0

# Coding group as factor and setting 'control' as the reference category.
df$group <- factor(
  df$group, levels = c(0, 1, 2), 
  labels = c(
    'control group',
    'dyadic action control', 
    'individual action control'
  )
)



table(df$group) / 14
table(df$sb0sex01)





```

## centering predictors

```{r centering}
df <- isolate(df, by = 'CoupleID',
            c("PSC_agent", "NSC_agent", "Sup_agent", "Sup_target", "time_spent", 
              "reldur", "sage", "page", "sbmi", "pbmi", "sbwwear", "pbwwear",
              'intention_agent_lagged', 'intention_target_lagged',
              'self_efficacy_agent_lagged', 'self_efficacy_target_lagged',
              'plan_agent_lagged', 'plan_target_lagged',
              'risk_perception_agent', 'risk_perception_target',
              'perceived_benfeits_agent', 'perceived_benfeits_target'),
            which='both')
```

# Exploring the data

```{r prepare for plotting}

# writing a function that allows changing the plot size per cell.
size <- function(width, height) {
    options(repr.plot.width = width, repr.plot.height = height)
    }

# writing a function that creates a title object for cowplots
title <- function(tit, plot_row,fs=20) {
    titleobject <- ggdraw() + draw_label(
            tit, x = 0, hjust = 0, fontface="bold", size = fs) +
            theme(plot.margin = margin(0,0,0,7))
    b <- plot_grid(
            titleobject, plot_row,
            ncol = 1,
            # rel_heights values control vertical title margins
            rel_heights = c(0.1, 1))
        return(b)
    }

```

## Basic plotting {.tabset}

### Boxplots

```{r boxplot}
scales <- c("PSC_agent", "NSC_agent", "Paff_target", "Paff_agent", "Naff_target", "Naff_agent")
mvpa <- c("sbwmvpa01", "pbwmvpa01" )

boxplot(df[,scales])
boxplot(df[,mvpa])
```

### Histograms outcomes

```{r histograms}
var_names <- c("sbwmvpa01", "pbwmvpa01", "Paff_target", "Paff_agent", "Naff_target", "Naff_agent")

for (var_name in var_names) {
  hist(df[[var_name]], main=var_name)
}

```

### Histograms predictors

```{r histograms 2}
var_names <- c("PSC_agent", "NSC_agent")

for (var_name in var_names) {
  hist(df[[var_name]], main=var_name)
}

```

## Correlations (within- and between person)

The package wbCorr and it's code is available on Github:
<https://github.com/Pascal-Kueng/wbCorr>

```{r prepare correlations, include=FALSE}
# Variables that vary both within and between should come first
vars_b <- c("PSC_agent", "NSC_agent", # For presentation purposes, Variables that vary both within and between person come first.
        "Paff_agent", "Paff_target", "Naff_agent", "Naff_target", "pbwmvpa01", "sbwmvpa01",
        "Sup_agent", "Sup_target", 
        "pbwwear", "sbwwear", "time_spent", 
        
        "intention_agent_lagged", "intention_target_lagged",
        "self_efficacy_agent_lagged", "self_efficacy_target_lagged",
        "risk_perception_agent", "risk_perception_target",
        "perceived_benfeits_agent", "perceived_benfeits_target",
        # Variables that vary only within come next
        "sbyday", "weeknd2",
        # Variables that vary only between person come last.
        "EG", "reldur", "sage", "page", "sbmi", "pbmi", "sb0sex01", "pb0sex01", "sb0kih01"
        ) 

# We create a vector of the full names, as we want them in the table. The order has to match the variables above.
var_names <- c("Exerted persuasion", "Exerted pressure",
"Positive affect agent", "Positive affect target", "Negative affect agent", "Negative affect target", "MVPA agent (in minutes)", "MVPA target (in minutes)",
"Provided support agent", "Provided support target",
"Wear time agent (in minutes)", "Wear time target (in minutes)", "Time spent together (in minutes)",

"Previous day's intention to be active today agent",
"Previous day's intention to be active today target",
"Previous day's self-efficacy for today agent",
"Previous day's self-efficacy for today target",
"Risk perception of not engaging in MVPA agent",
"Risk perception of not engaging in MVPA target",
"Perceived benefits of MVPA agent",
"Perceived benefits of MVPA target",


"Day", "Weekend (no = 0; yes = 1)",
"Intervention group (no = 0; yes = 1)", "Relationship length (years)", "Age target (years)", "Age agent (years)", "BMI target (kg/m2)", "BMI agent (kg/m2)", "Gender target (female = 0; male = 1)", "Gender agent (female = 0; male = 1)", "Kids (no = 0; yes = 1)")

df_cors <- df[vars_b]
colnames(df_cors) <- var_names
```

```{r prepare small correlation table, include=FALSE}
# small corr table
vars_b_small <- c("PSC_agent", "NSC_agent", # For presentation purposes, Variables that vary both within and between person come first.
        "Paff_agent", "Paff_target", "Naff_agent", "Naff_target", "pbwmvpa01", "sbwmvpa01",
        "Sup_agent", "Sup_target", 
        "pbwwear", "sbwwear", "time_spent", 
        # Variables that vary only within come next
        "sbyday", "weeknd2"
        ) 

# We create a vector of the full names, as we want them in the table. The order has to match the variables above.
var_names_small <- c("Persuasion agent", "Pressure agent",
"Positive affect agent", "Positive affect target", "Negative affect agent", "Negative affect target", "MVPA agent (in minutes)", "MVPA target (in minutes)",
"Provided support agent", "Provided support target",
"Wear time agent (in minutes)", "Wear time target (in minutes)", "Time spent together (in minutes)", 
"Day", "Weekend (no = 0; yes = 1)")

df_cors_small <- df[vars_b_small]
colnames(df_cors_small) <- var_names_small
```

```{r compute correlations with wbCorr}
wbCorrObject <- wbCorr(df_cors, df$CoupleID)
wbCorrObject_small <- wbCorr(df_cors_small, df$CoupleID)

cor_matrix <- summary(wbCorrObject, which = 'wb')
cor_matrix_small <- summary(wbCorrObject_small, 'wb')

wbCorr::to_excel(cor_matrix, "correlation_matrices.xlsx")
wbCorr::to_excel(cor_matrix_small, "correlation_matrices_small.xlsx")

cor_matrix
cor_matrix_small

```

## Descriptives

```{r descriptivestatistics}
# Stats for all Vars with the full DF
vars_stats <- setdiff(vars_b, c("sb0sex01", "pb0sex01", "sb0kih01"))

as.data.frame(report_table(df[,vars_stats]))

```

```{r desc2}

as.data.frame(report_table(df$reldur))

```


# Save datasets

```{r}


# Only save the variables we need for furhter analyses for data protection reasons. 

# Define the list of variables to keep
variables_to_keep <- c(
  'ppysko06', 'ppysko09', 'ppysko21', 'ppysko25',
  'ppysko03', 'ppysko11', 'ppysko26', 'ppysko29',
  
  'CoupleID', 'PSC_agent', 'NSC_agent', 'PSC_agent_cw', 'NSC_agent_cw', 'sbyday', 'weeknd2', 
  'PSC_agent_cb', 'NSC_agent_cb', 'sbwmvpa01', 'sbwwear_cw', 'sbwwear_cb', 
  'sbwwear', 'pbwwear',
  'pbwmvpa01', 'pbwwear_cw', 'pbwwear_cb', 'Sup_agent_cw', 'Sup_target_cw', 
  'time_spent_cw', 'intention_agent_lagged_cw', 'intention_target_lagged_cw', 
  'self_efficacy_agent_lagged_cw', 'self_efficacy_target_lagged_cw', 
  'plan_agent_lagged_cw', 'plan_target_lagged_cw', 'risk_perception_agent_cw', 
  'risk_perception_target_cw', 'perceived_benfeits_agent_cw', 
  'perceived_benfeits_target_cw', 'Sup_agent_cb', 'Sup_target_cb', 
  'time_spent_cb', 'intention_agent_lagged_cb', 'intention_target_lagged_cb', 
  'self_efficacy_agent_lagged_cb', 'self_efficacy_target_lagged_cb', 
  'plan_agent_lagged_cb', 'plan_target_lagged_cb', 'risk_perception_agent_cb', 
  'risk_perception_target_cb', 'perceived_benfeits_agent_cb', 
  'perceived_benfeits_target_cb', 'reldur_cb', 'page', 'sage', 'pbmi', 'sbmi', 
  'sb0kih01', 'pb0kih01', 'sb0sex01', 'pb0sex01', 'group', 'Paff_target', 'Naff_target', 
  'Paff_agent', 'Naff_agent'
)





df_og <- df
# Subset the dataframe
df_subset <- df_og %>% select(all_of(variables_to_keep))

# Save the subset to an RDS file for OSF
saveRDS(df_subset, file = 'DataSet_Subset.rds')


```




```{r}
report::report_system()

```

```{r results='asis'}
report::report_packages()

```

```{r results='asis'}
report::cite_packages()

```