---
title: "Health-Related Social Influence Strategies in Overweight Romantic Couples: Daily Associations with Physical Activity and Affect for Targets and Actors "
author: "Pascal Küng, MSc (ORCID: 0000-0001-7346-9414), Corina Berli, PhD (ORCID: 0000-0002-5078-3539), Patrick S. Höhener, MSc (ORCID: 0000-0003-3635-2799), Robert Tobias, PhD (ORCID: 0000-0001-7972-122X), Urte Scholz, PhD (ORCID: 0000-0003-0184-5921)"
date: "`r Sys.Date()`"
output: 
  html_document: 
    df_print: kable
    toc: yes
    toc_float: yes
    code_folding: show
    toc_depth: 5
---

# Setup and loading

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
options(dplyr.print_max = 100)

library('ggplot2')
library('nlme')
library('MASS')
library('haven')
library('scales')
library('cowplot')
library('devtools')
library('ggResidpanel')
library('lme4')
library('glmmTMB')
library('DHARMa')
library('ggeffects')
library('broom.mixed')
library('easystats')
library('Hmisc')
library('bmlm')
library('tidyverse')
library('wbCorr')
library('psych')
library('report')
library('lavaan')
library('basicPlotteR')
library('misty')
library('dplyr')

```

```{r loading_datasets, results='hide'}

df <- readRDS(file = 'DataSet_Subset.rds')
  
```


# Modelling

We define the following functions to facilitate reporting of the models.

```{r function to report models in a standardized way}

# Defining common elements
common_within_person_effects <- c(
  '(Intercept)',
  '---WITHIN-PERSON EFFECTS---',
  '---PSC---',
  'ppysko06_cw',
  'ppysko09_cw', 
  'ppysko21_cw',
  'ppysko25_cw', 
  '---NSC---',
  'ppysko03', 
  'ppysko11', 
  'ppysko26', 
  'ppysko29', 
  '---Covariates---',

  'sbyday', 
  'weeknd2', 
  'weartime_cw'
)

common_between_person_effects <- c(
  'PSC_agent_cb', 
  'NSC_agent_cb', 
  'weartime_cb'
)

common_random_effects <- c(
  'Std.Dev.(Intercept)|CoupleID', 
  'Std.Dev.PSC_agent_cw|CoupleID', 
  'Std.Dev.NSC_agent_cw|CoupleID', 
  'Cor.PSC_agent_cw.(Intercept)|CoupleID', 
  'Cor.NSC_agent_cw.(Intercept)|CoupleID', 
  'Cor.NSC_agent_cw.PSC_agent_cw|CoupleID'
)

common_model_info <- c(
  'Within-group standard error', 
  'dispersion', 
  'AR1'
)

# Order for report
order_rep <- c(
  common_within_person_effects, 
  '---BETWEEN-PERSON EFFECTS---',
  common_between_person_effects, 
  '---RANDOM-EFFECTS---',
  common_random_effects,
  '---------MODEL INFO---------',
  common_model_info
)

# Order for sensitivity analysis
order_sens <- c(
  common_within_person_effects, 
  'Sup_agent_cw', 
  'Sup_target_cw', 
  'time_spent_cw',
  'intention_agent_lagged_cw',
  'intention_target_lagged_cw',
  'self_efficacy_agent_lagged_cw',
  'self_efficacy_target_lagged_cw',
  'plan_agent_lagged_cw',
  'plan_target_lagged_cw',
  'risk_perception_agent_cw', 
  'risk_perception_target_cw',
  'perceived_benfeits_agent_cw',
  'perceived_benfeits_target_cw',
  '---BETWEEN-PERSON EFFECTS---',
  common_between_person_effects, 
  'Sup_agent_cb', 
  'Sup_target_cb', 
  'time_spent_cb', 
  'intention_agent_lagged_cb',
  'intention_target_lagged_cb',
  'self_efficacy_agent_lagged_cb',
  'self_efficacy_target_lagged_cb',
  'plan_agent_lagged_cb',
  'plan_target_lagged_cb',
  'risk_perception_agent_cb', 
  'risk_perception_target_cb',
  'perceived_benfeits_agent_cb',
  'perceived_benfeits_target_cb',
  'reldur_cb', 
  'page', 
  'sage', 
  'pbmi', 
  'sbmi', 
  'sb0kih01',
  'sb0sex01',
  'pb0sex01',
  'groupdyadic action control',
  'groupindividual action control',
  '---RANDOM-EFFECTS---',
  common_random_effects,
  '---------MODEL INFO---------',
  common_model_info
)



full_report <- function(model, order) {
  if (class(model) == 'glmmTMB') {
    return(report_glmmTMB(model, order))
  } else {
    return(report_nlme(model, order))
  }
}


report_glmmTMB <- function(model, order) {
  # Extracting model parameters and creating the initial dataframe
  rep_df <- as.data.frame(model_parameters(model, exponentiate = TRUE))[,c('Parameter', 'Coefficient', 'SE', 'p', 'CI_low', 'CI_high', 'Effects', 'Component')]
  
  # Removing rows where the Parameter includes 'factor'
  rep_df <- rep_df[rep_df$Effects != 'random',]
  
  
  # Adding confidence intervals
  
  int <- as.data.frame(confint(model))
  
  intt <- int[!grepl('factor', rownames(int)),]
  intervals <- intt[grepl('CoupleID', rownames(intt)),]
  
  
  df_intervals <- data.frame('Parameter' = rownames(intervals),
                             'Coefficient' = intervals$Estimate,
                             'SE' = NA, 
                             'CI_low' = intervals$`2.5 %`,
                             'CI_high' = intervals$`97.5 %`, 
                             'p' = NA, 
                             'Effects' = 'random', 
                             'Component' = 'conditional')
  
  rep_df <- rbind(rep_df, df_intervals)
  
  
  # Extracting the AR1 coefficient from the model
  ar1 <- capture.output(summary(model)$varcor)
  if (length(grep("ar1", ar1)) > 0) {
    ar1_value <- as.numeric(strsplit(ar1[grep("ar1", ar1)], "\\(ar1\\)")[[1]][2])
  } else {
    ar1_value <- NA
  }
  
  
  # Combining and reporting
  
  rep_df <- rep_df %>% 
    add_row(Parameter = '---WITHIN-PERSON EFFECTS---') %>%
    add_row(Parameter = '---BETWEEN-PERSON EFFECTS---') %>%
    add_row(Parameter = '---RANDOM-EFFECTS---') %>%
    add_row(Parameter = 'Within-group standard error') %>%
    add_row(Parameter = '---------MODEL INFO---------') %>%
    add_row(Parameter = 'AR1', Coefficient = ar1_value)
    
  rep_df
  rep_df[rep_df$Component == 'dispersion' & rep_df$Parameter == '(Intercept)', ]$Parameter <- 'dispersion'
  

  # Reorder the dataframe based on 'order'
  rep_df$Parameter[rep_df$Parameter == "sbwwear_cw"] <- 'weartime_cw'
  rep_df$Parameter[rep_df$Parameter == "sbwwear_cb"] <- 'weartime_cb'
  rep_df$Parameter[rep_df$Parameter == "pbwwear_cw"] <- 'weartime_cw'
  rep_df$Parameter[rep_df$Parameter == "pbwwear_cb"] <- 'weartime_cb'
  
  
  rep_df <- rep_df[match(order, rep_df$Parameter),]
  
  # Call function for rounding and adding stars
  rep_df <- process_coefficients(rep_df)
  
  
  return(rep_df)
}



report_nlme <- function(model, order) {
  # Extracting fixed effects
  rep_df <- as.data.frame(model_parameters(model))[,c('Parameter', 'Coefficient', 'SE', 'p', 'CI_low', 'CI_high', 'Effects')]
  
  rep_df <- tryCatch({
  
      # Confidence intervals of random effects
      int <- intervals(model)
      int_rand <- as.data.frame(int$reStruct)
      
      # add AR1
      int_ar1 <- as.data.frame(int$corStruct)
      
      if (nrow(int_ar1) > 0) {
        rownames(int_ar1) <- c('AR1')
        colnames(int_ar1) <- colnames(int_rand)
        int_rand <- rbind(int_rand, int_ar1)
      } else {
        # Create a row with NA values
        na_row <- setNames(data.frame(matrix(NA, ncol = ncol(int_rand), nrow = 1)), colnames(int_rand))
        rownames(na_row) <- 'AR1'
        int_rand <- rbind(int_rand, na_row)
      }
      
      # Add Confint for sigma
      int_resid <- as.data.frame(int$sigma)
      
      int_rand[nrow(int_rand) + 1,] <- c(int_resid[1, 1], int_resid[2, 1], int_resid[3, 1])
      rownames(int_rand)[nrow(int_rand)] <- 'Within-group standard error'
    
      
    
      
      # Construct df
      
      int_df <- data.frame(
        Parameter = rownames(int_rand),
        Coefficient = int_rand$CoupleID.est.,
        SE = NA,
        CI_low = int_rand$CoupleID.lower,
        CI_high = int_rand$CoupleID.upper,
        p = NA, 
        Effects = 'random'
      )
      
      # Combine
      rep_df <- rep_df[rep_df$Effects != 'random',]
      
      rep_df <- rbind(rep_df, int_df)
      rep_df$Parameter[rep_df$Parameter == 'sd((Intercept))'] <- 'Std.Dev.(Intercept)|CoupleID'
      rep_df$Parameter[rep_df$Parameter == 'sd(PSC_agent_cw)'] <- 'Std.Dev.PSC_agent_cw|CoupleID'
      rep_df$Parameter[rep_df$Parameter == 'sd(NSC_agent_cw)'] <- 'Std.Dev.NSC_agent_cw|CoupleID'
      rep_df$Parameter[rep_df$Parameter == 'cor((Intercept),PSC_agent_cw)'] <- 'Cor.PSC_agent_cw.(Intercept)|CoupleID'
      rep_df$Parameter[rep_df$Parameter == 'cor((Intercept),NSC_agent_cw)'] <- 'Cor.NSC_agent_cw.(Intercept)|CoupleID'
      rep_df$Parameter[rep_df$Parameter == 'cor(PSC_agent_cw,NSC_agent_cw)'] <- 'Cor.NSC_agent_cw.PSC_agent_cw|CoupleID'
      rep_df$Parameter[rep_df$Parameter == 'cor(NSC_agent_cw,PSC_agent_cw)'] <- 'Cor.NSC_agent_cw.PSC_agent_cw|CoupleID'
      rep_df
    }, error = function(e) {
      rep_df$Parameter[rep_df$Parameter == "SD (Intercept)"] <- 'Std.Dev.(Intercept)|CoupleID'
      rep_df$Parameter[rep_df$Parameter == 'SD (PSC_agent_cw)'] <- 'Std.Dev.PSC_agent_cw|CoupleID'
      rep_df$Parameter[rep_df$Parameter == 'SD (NSC_agent_cw)'] <- 'Std.Dev.NSC_agent_cw|CoupleID'
      rep_df$Parameter[rep_df$Parameter == 'Cor (Intercept~PSC_agent_cw)'] <- 'Cor.PSC_agent_cw.(Intercept)|CoupleID'
      rep_df$Parameter[rep_df$Parameter == 'Cor (Intercept~NSC_agent_cw)'] <- 'Cor.NSC_agent_cw.(Intercept)|CoupleID'
      rep_df$Parameter[rep_df$Parameter == 'Cor (PSC_agent_cw~NSC_agent_cw)'] <- 'Cor.NSC_agent_cw.PSC_agent_cw|CoupleID'
      rep_df$Parameter[rep_df$Parameter == 'Cor (NSC_agent_cw~PSC_agent_cw)'] <- 'Cor.NSC_agent_cw.PSC_agent_cw|CoupleID'
      rep_df$Parameter[rep_df$Parameter == 'SD (Observations)'] <- 'Within-group standard error'
      rep_df
    }
  )
  
  # Finishing touches
  rep_df <- rep_df %>% 
    add_row(Parameter = '---WITHIN-PERSON EFFECTS---') %>%
    add_row(Parameter = '---BETWEEN-PERSON EFFECTS---') %>%
    add_row(Parameter = '---RANDOM-EFFECTS---') %>%
    add_row(Parameter = '---------MODEL INFO---------') %>%
    add_row(Parameter = 'dispersion') %>%
    add_row(Parameter = 'sbwwear_cb') %>%
    add_row(Parameter = 'sbwwear_cw')
  
  
  # Reorder the dataframe based on 'order'
  rep_df <- rep_df[match(order, rep_df$Parameter),]
  
  # Call function for rounding and adding stars
  rep_df <- process_coefficients(rep_df)
  
  return(rep_df)
}





process_coefficients <- function(df) {
  # Round
  df[, c(2, 3, 5, 6)] <- round(df[, c(2, 3, 5, 6)], 2)
  df[, 4] <- round(df[, 4], 3)

  # Add stars
  df$Coefficient <- as.character(sprintf("%.2f", df$Coefficient))
  df$Coefficient <- ifelse(is.na(df$p), df$Coefficient,
                           ifelse(df$p < 0.001, paste0(df$Coefficient, "***"),
                                  ifelse(df$p < 0.01, paste0(df$Coefficient, "**"),
                                         ifelse(df$p < 0.05, paste0(df$Coefficient, "*"), 
                                                df$Coefficient))))
  return(df)
}



```

## Models

### Models for TARGET

#### Positive Affect - Target


```{r}

persuasion_vars <- c('ppysko06', 'ppysko09', 'ppysko21', 'ppysko25')
pressure_vars <- c('ppysko03', 'ppysko11', 'ppysko26', 'ppysko29')

df <- bmlm::isolate(
  df, 
  by = 'CoupleID',
  value = c(persuasion_vars, pressure_vars),
  which = 'both'
)
  
```


```{r base1}
# Base Model
posaff_target <- lme(
    fixed = Paff_target~
        ppysko06_cw + ppysko09_cw + ppysko21_cw + ppysko25_cw + 
        ppysko03_cw + ppysko11_cw + ppysko26_cw + ppysko29_cw +
        sbyday + weeknd2 +
        PSC_agent_cb + NSC_agent_cb,
    data = as.data.frame(df),
    random = ~ 1 | CoupleID,
    #correlation = corAR1(form = ~ 1 | CoupleID),
    na.action = na.omit,
    control = lmeControl(opt='optim',
                         maxIter = 1e4,
                         msMaxEval = 1e4)
)

check_singularity(posaff_target)
#performance::check_model(posaff_target)

summary(posaff_target)

```

none

#### Negative Affect - Target



```{r base2}
### Base model for negative affect target
negaff_target <- lme(
  fixed = Naff_target ~
        ppysko06_cw + ppysko09_cw + ppysko21_cw + ppysko25_cw + 
        ppysko03_cw + ppysko11_cw + ppysko26_cw + ppysko29_cw +
        sbyday + weeknd2 +
        PSC_agent_cb + NSC_agent_cb,
  data = as.data.frame(df),
  random = ~ 1 | CoupleID,
  #correlation = corAR1(form = ~ 1 | CoupleID),
  na.action = na.omit,
  control = lmeControl(opt='optim',
                         maxIter = 1e4,
                         msMaxEval = 1e4)
)

check_singularity(negaff_target)
#performance::check_model(negaff_target)

summary(negaff_target)
```
none


#### MVPA - Target


```{r mvpa2}
mvpa_target <- glmmTMB(
  sbwmvpa01 ~
    ppysko06_cw + ppysko09_cw + ppysko21_cw + ppysko25_cw + 
    ppysko03_cw + ppysko11_cw + ppysko26_cw + ppysko29_cw +
    sbyday + weeknd2 +
    PSC_agent_cb + NSC_agent_cb + 
    sbwwear_cw + sbwwear_cb + 
    
    (1 | CoupleID) +
    ar1(factor(sbyday) - 1 | CoupleID),
    family = nbinom1,
    data = df,
    control = glmmTMBControl(optArgs = list(iter.max = 1e4, eval.max = 1e4))
)
check_singularity(mvpa_target)

simResids <- simulateResiduals(mvpa_target, nSim=1005)
plot(simResids)

summary(mvpa_target)
```

21, almost 03, almost 06, 

### Models for AGENT

How is the use of persuasion and pressure associated with outcomes in
the user?

#### Positive affect - Agent

```{r posaff1}
posaff_agent <- lme(
  fixed = Paff_agent ~
        ppysko06_cw + ppysko09_cw + ppysko21_cw + ppysko25_cw + 
        ppysko03_cw + ppysko11_cw + ppysko26_cw + ppysko29_cw +
        sbyday + weeknd2 +
        PSC_agent_cb + NSC_agent_cb,
  data = as.data.frame(df),
  random = ~ 1 | CoupleID,
  correlation = corAR1(form = ~ 1 | CoupleID),
  na.action = na.omit,
  control = lmeControl(opt='optim',
                      maxIter = 1e4,
                      msMaxEval = 1e4)
)
check_singularity(posaff_agent)
#performance::check_model(posaff_agent)

summary(posaff_agent)
```

21, 25, 26

#### Negative Affect - Agent

Ar1 had to be removed to achieve convergence.

```{r posaff3}
### Base model for negative affect target
# Specifying model for Negative Affect
negaff_agent <- lme(
  fixed = Naff_agent ~
        ppysko06_cw + ppysko09_cw + ppysko21_cw + ppysko25_cw + 
        ppysko03_cw + ppysko11_cw + ppysko26_cw + ppysko29_cw +
        sbyday + weeknd2 +
        PSC_agent_cb + NSC_agent_cb,
  data = as.data.frame(df),
  random = ~ 1 | CoupleID,
  #correlation = corAR1(form = ~ 1 | CoupleID),
  na.action = na.omit,
  control = lmeControl(opt='optim',
                         maxIter = 1e4,
                         msMaxEval = 1e4)
)
check_singularity(negaff_agent)
#performance::check_model(negaff_agent)

summary(negaff_agent)
```

Almost 25, yes 26


#### MVPA - Agent

```{r mvpa_agent2}
# Base Model (not converging)
mvpa_partner <- glmmTMB(
    pbwmvpa01 ~
      ppysko06_cw + ppysko09_cw + ppysko21_cw + ppysko25_cw + 
      ppysko03_cw + ppysko11_cw + ppysko26_cw + ppysko29_cw +
      sbyday + weeknd2 +
      PSC_agent_cb + NSC_agent_cb + 
      pbwwear_cw + pbwwear_cb + 
      (1 | CoupleID),
    family = nbinom1,
    data = df,
    control = glmmTMBControl(optimizer = nlminb, 
                             optArgs = list(iter.max = 1e4, 
                                            eval.max = 1e4))
)
check_singularity(mvpa_partner)
simResids <- simulateResiduals(mvpa_partner, nSim = 1005)
plot(simResids)

summary(mvpa_partner)
```

only 25
